Decentralized Data Marketplace to Enable Trusted Machine Economy

### 2019-08-28 paper.tex
Reword and add citations

\subsubsection{smart contract}
Smart contract\cite{smartContract} is a protocol for formulating agreement on blockchain that provides verification and execution of the contract. The code in the smart contract could interact with other contracts, make decisions, store data and transfer cryptocurrency. All conditions and states established in the contract are transparent and with enforcement. The appearance of smart contracts makes trading more flexible, and achieves more complex trading patterns in reality.

@@

\subsubsection{TangleID}
TangleID\cite{TangleID} is a self-soverign identity system based on IOTA, the goal is to establish a solution that do not require any third-party authority to verify an identity and its digital footprint. In TangleID, the digital footprint is converted into digital assets with the principle of Decentralized Identifiers (DIDs) defined by W3C, and by putting DID documents on MAM makes TangleID a GDPR-Complianced system. Each identity has a public/private key pair recorded on MAM, it is used in digital signature for identity authentication. With every participant in data marketplace registers on TangleID, one can easily verify data provider's identity and data integrity with the public key on the DID document, and that we can ensure the reliability of data sources.

>>>>

\subsubsection{Ethereum Smart Contract}
Smart contract\cite{smartContract} is a protocol for formulating agreement on blockchain that provides verification and execution of the contract. The code in the smart contract could interact with other contracts, make decisions, store data and transfer cryptocurrency. All conditions and states established in the contract are transparent and with enforcement. The appearance of smart contracts makes trading more flexible, and achieves more complex trading patterns in reality.

@@

\subsubsection{TangleID}
TangleID\cite{TangleID} is a self-soverign identity system based on IOTA, the goal is to establish a solution that do not require any third-party authority to verify an identity and its digital footprint. In TangleID, the digital footprint is converted into digital assets with the principle of Decentralized Identifiers (DIDs)\cite{DID} defined by W3C, and by putting DID documents on MAM makes TangleID a GDPR-Complianced system. Each identity has a public/private key pair recorded on MAM, it is used in digital signature for identity authentication. With every participant in data marketplace registers on TangleID, one can easily verify data provider's identity and data integrity with the public key on the DID document, and that we can ensure the reliability of data sources.
